\documentclass{article}

\usepackage[backend=biber]{biblatex}
\addbibresource{first.bib}
\usepackage[margin=2cm]{geometry}
\usepackage{titling}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\title{Algorithm For D-ARPSpoof}

\renewcommand{\maketitle}{

	\begin{center}
		{\huge\noindent\ignorespaces\textbf{\thetitle}\par}
	\end{center}
	\vspace{0.3in}
	
}
\begin{document}
\maketitle

\section{Data Structures Used}

\begin{enumerate}
	\item HashMap$<$DatapathId,HashMap$<$OFPort,$<$Vlan, IP, Mac$>$$>$ : portIpMap
	\item HashMap$<$MacAddress,Switch-Port$>$ : macPortMap
\end{enumerate}

\section{Algorithm}


\subsection{Handling Packet-IN DHCP Messages}


\subsubsection{Updating Data Structures} \label{dhcp-ds}


\begin{itemize}
	\item \textbf{DHCP REQUEST}

		\begin{enumerate}
			\item Delete mapped mac-port pair from macPortMap with mac equals source MAC of incoming Packet.
			\item If portIpMap has entry for inPort then delete that entry.
			\item If macPortMap does not have any entry for incoming packet's source MAC Address, then add those entry in macPortMap.
		\end{enumerate}
	\item \textbf{DHCP ACKNOWLEDGEMENT} \label{dhcp-ack}
		\begin{enumerate}
			\item Get Switch-Port pair from macPortMap for destination mac address and name that as pair.
			\item Add following entry in portIpMap:

				\small{
					$<$\textit{pair.switch} ,  \textit{pair.port} , vid , dhcpPayload.yourIPAddress , destination-MAC$>$
				}
		\end{enumerate}

\end{itemize}


\subsubsection{Updating Flow Rules}

\begin{itemize}
	\item \textbf{DHCP REQUEST}

		\begin{enumerate}
			\item If portIpMap has entry for received switch and input port then remove flow entry from current switch with :

				\begin{itemize}
					\item inPort : incomingPacket's input port.
					\item etherType: ARP
				\end{itemize}
				
		\end{enumerate}
	\item \textbf{DHCP ACKNOWLEDGEMENT}

		\begin{enumerate}
			\item Get Switch-Port pair from macPortMap for destination mac address and name that as pair.
			\item Then add a flow rule to block all ARP packet from the  current input port. Write this flow with priority 10.
			\item Add flow in \textit{pair.switch} to direct the packet with 

				\begin{itemize}

					\item IP address : dhcp-payload's yourIPAddress
					\item vlan-vid : incomingPacket's vlan id 
					\item inPort : \textit{pair.port}
				\end{itemize}

				to goto flow table 1 of \textit{pair.switch} . Write this flow with priority 20.
		\end{enumerate}
		
\end{itemize}




\subsection{Handling DHCP-ACK PacketOut Messages}

Same as section \ref{dhcp-ds} DHCP ACKNOWLEDGEMENT handling.

\subsection{Handling ARP}

\begin{enumerate}
	\item Check for packet's target protocol address and vlan id in ipPortTable. If not present then drop it otherwise get $<$Switch-Port$>$ pair associated with it. Name it destination.
	\item Get $<$Switch-Port$>$ pair associated with packet's sender protcol address and vlan id. Name it source.
	\item Get the path from source to destination using routing service and name it `path'.
	\item Install the rules as:
		\begin{lstlisting}
			Match m = (EtherType,ARP) + (Vlan-id , Packet vlan-id)+(ArpTargetProtocolAddress , Packet ArpTargetProtocolAddress);
			List<SwitchPortPair> list = path;
			for(index = list.size-1;index>0;index-=2){
				installFlowRule(table-id=2, match=m, switch=list[index].switch, priority=30, action=output(list[index].port);
			}
			pushOFPacketOut(switch=curSwitch, packet=packet-in, outPort=list[1].port, inPort=list[0].port);
		\end{lstlisting}
\end{enumerate}

\subsection{Handling Switch Added event}

\begin{enumerate}
	\item Write flow rule to forward all ARP packets to controller in flow table 1 of added switch with priority 0. (Default flow for table 1) 
\end{enumerate}



\subsection{Handling Switch Removed event}

\begin{enumerate}
	\item Remove all entry of removed swith from portIpMap
	\item Also, Remove all entry of removed switch from macPortMap.
\end{enumerate}

\subsection{Handling link update}

\begin{enumerate}
	\item If any of source switch-port pair and destination switch-port pair exist in our portIPMap, and update type is direct link, then:
		\begin{itemize}
			\item If source switch exist in switch port pair:
				\begin{enumerate}
					\item remove any flow matching inPort to be source port from the respective source switch.
					\item remove the mac from macPortMap associated with that switch port pair.
					\item remove the switch-port pair from portIpMap also.
				\end{enumerate}
			\item If destination switch exist in switch port pair:
				\begin{enumerate}
					\item remove any flow matching inPort to be destination port from the respective destination switch.
					\item remove the mac from macPortMap associated with that switch port pair.
					\item remove the switch-port pair from portIpMap also.
				\end{enumerate}
		\end{itemize}
		
		
\end{enumerate}

\printbibliography
\end{document}
